Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-04-30 paper/paper.tex

\subsection{Web Application}
{\color{red}\textbf{NOT COMPLETE}}
As mentioned in section 1.2, the ACMx group has already created a web application that will display the data collected from the sensors in the system. The site is currently accessible online at \url{http://acmxlabs.org/parking/}. Since the current site is essentially just a shell with no data, one main goal of this project is to make the main pages of the site fully functional. Another main goal is to create an administrator side to the site, where data can be viewed and updated by site administrators. The main focus of this subsystem will be to provide interfaces for both general users and administrators that make the data we collect both useful and easy to access. Since the ACMx team already has some protocols in place for collecting and displaying the data from the magnetometer Arduino Fios, the ACMx team will continue development on this interface, and our group will focus on other parts of the application, as described below. The web application itself will be written with PHP on the back end and HTML5/CSS3/JavaScript on the front end. The following subsections describe the various pieces of the site that we aim to complete during this project.

>>>>

\subsection{Web Application}

Prior to the start of our project, the ACMx group created a web application designed to display the data collected from the sensors in the parking lot monitoring system. Since the current site was essentially just a shell with no data, one main goal of this project was to improve the website. The site consists of three main parts:

\begin{enumerate}
\item Front-facing, publicly-accessible 'Smartlots' website,
\item Administrator website, and
\item Back-end HTTP interface.
\end{enumerate}

The Smartlots website makes use of the magnetometer sensors; it provides maps showing the number of cars in each parking lot, maintains lists of parking lots, and lists usage statistics about each lot. The administrator website provides tools for system administrators. These tools are described in detail below. Before we started this project, the ACMx group had already created the publicly-accessible Smartlots interface. Therefore, we chose to focus on creating the administrator side of the site, and improving the back-end of the entire site to make it more secure and easier to extend in the future.

This subsystem encompasses several components, each of which helps to accomplish our goal of providing campus members with a better parking experience. The interfaces for both general users and administrators make the data we collect both useful and easy to access. The web application itself is written with PHP on the back end and HTML5/CSS3/JavaScript on the front end. The following subsections describe the various pieces of the site that we completed this project.

\subsubsection{RESTful HTTP Interface}
The base station Raspberry Pi needs some way to communicate its data with the web application. The application uses a MySQL database to store the sensor data; this database is described below. The simplest way to meet this need is to create an HTTP interface on the server. We will need this interface to handle requests from the front end of the web application anyway, and so it makes sense to also allow the base station to communicate with our server through HTTP requests. We will create a REST-ful HTTP interface that corresponds closely to the database schema and the front-end of the webpage, and the base station will send all its data to the application via the same interface. For example, if an image of a license plate is detected, the base station would send an HTTP POST request to 'acmxlabs.org/parking/licenseImage' (actual urls may change when we start designing the interface), and the server would receive the request and send the image to the ALPR software, as described in section 2.5. When the web application needs to get the data associated with a license plate, it will send an HTTP GET request to 'acmxlabs.org/parking/licensePlate/123ABC'.

{\color{red}\textbf{NOT COMPLETE}}
As mentioned in section 1.2, the ACMx group has already created a web application that will display the data collected from the sensors in the system. The site is currently accessible online at \url{http://acmxlabs.org/parking/}. Since the current site is essentially just a shell with no data, one main goal of this project is to make the main pages of the site fully functional. Another main goal is to create an administrator side to the site, where data can be viewed and updated by site administrators. The main focus of this subsystem will be to provide interfaces for both general users and administrators that make the data we collect both useful and easy to access. Since the ACMx team already has some protocols in place for collecting and displaying the data from the magnetometer Arduino Fios, the ACMx team will continue development on this interface, and our group will focus on other parts of the application, as described below. The web application itself will be written with PHP on the back end and HTML5/CSS3/JavaScript on the front end. The following subsections describe the various pieces of the site that we aim to complete during this project.
